Python as a machine learning language: experiences from the \sklearn project

### 2013-06-10 paper.tex
page numbers
capitalization

@@

\textbf{Transformers.} Since it is common to modify or filter data before
feeding it to a learning algorithm, some estimators in the library implement a
\textit{transformer} interface which defines a \texttt{transform} method. It
takes as input some new data \texttt{X\_test} and yields as output a transformed
version of \texttt{X\_test} Preprocessing, feature selection and dimensionality
reduction algorithms are all provided as transformers within the library.  In
our example, if one wanted to preprocess the inputs \texttt{X\_train} before
fitting the logistic regression estimator, e.g., by standardizing the feature
values, one could thus simply write:
\begin{verbatim}
from sklearn.preprocessing import StandardScaler
scaler = StandardScaler()
scaler.fit(X_train)
X_train = scaler.transform(X_train)
\end{verbatim}
Of course, in practice, it is important to apply the same preprocessing to the
test data \texttt{X\_test}. This can easily be done as follows:
\begin{verbatim}
X_test = scaler.transform(X_test)
\end{verbatim}
Transformers also include a variety of learning algorithms, such as
dimension reduction (PCA, manifold learning techniques), Kernel
approximation techniques, and any other approach that can be used to
derive a modified representation of the data.

>>>>

\pagestyle{headings}

@@

\textbf{Transformers.} Since it is common to modify or filter data before
feeding it to a learning algorithm, some estimators in the library implement a
\textit{transformer} interface which defines a \texttt{transform} method. It
takes as input some new data \texttt{X\_test} and yields as output a transformed
version of \texttt{X\_test} Preprocessing, feature selection and dimensionality
reduction algorithms are all provided as transformers within the library.  In
our example, if one wanted to preprocess the inputs \texttt{X\_train} before
fitting the logistic regression estimator, e.g., by standardizing the feature
values, one could thus simply write:
\begin{verbatim}
from sklearn.preprocessing import StandardScaler
scaler = StandardScaler()
scaler.fit(X_train)
X_train = scaler.transform(X_train)
\end{verbatim}
Of course, in practice, it is important to apply the same preprocessing to the
test data \texttt{X\_test}. This can easily be done as follows:
\begin{verbatim}
X_test = scaler.transform(X_test)
\end{verbatim}
Transformers also include a variety of learning algorithms, such as
dimension reduction (PCA, manifold learning techniques), kernel
approximation techniques, and any other approach that can be used to
derive a modified representation of the data.
